New lower bounds for Schur and weak Schur numbers

### 2021-04-07 article/article.tex
remarkgit add .git add .git add .git add .git add .git add .git add .git add .

\newtheorem{definition}{Definition}[section]
\newtheorem{notation}[definition]{Notation}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{computational theorem}{Computational Theorem}[section]
\newtheorem{corollary}{Corollary}[theorem]

@@

@@

\subsection{Weak Schur number five}
As explained in the previous subsection, the search space used for showing that  \(WS(5) \geq 196\) may not contain optimal solution. In this subsection, 
we give necessary conditions for a hypothetical partition of \([\![1,197]\!]\) in 5 weakly sum-free subsets using the same method as the previous subsection.

>>>>

\newtheorem{definition}{Definition}[section]
\newtheorem{notation}[definition]{Notation}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{computational theorem}{Computational Theorem}[theorem]
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{remark}{Remark}[section]

@@

\begin{remark}
The performance of
\end{remark}

@@

\subsection{Weak Schur number five}
As explained in the previous subsection, the search space used for showing that  \(WS(5) \geq 196\) may not contain optimal solution. In this subsection, 
we give necessary conditions for a hypothetical partition of \([\![1,197]\!]\) in 5 weakly sum-free subsets using the same type of methods as in the
 previous subsection.

\par
First

\begin{computational theorem}
If there exists a partition of \([\![1,197]\!]\) in 5 weakly sum-free subsets then \(m_5 \leq\). 
\end{computational theorem}

More precisely, we verified the following results using the glucose SAT solver [reference].

\begin{tabular}{| c | *{21}{ p{2mm} |}}
	\hline
	\(m_4\)                   &   4   &   5   &   6  &   7   &   8   &   9   &  10  &  11  &  12  &  13  &  14  &  15  &  16  &  17  &  18  &  19  &  20  &  21  &  22  &  23  &  24  \\ 
	\hline
	\(WS(4 | m_4) + 1\) &  55  &  59  &  60  &  59  &  59  &  60  &  60  &  60  &  60  &  64  &  63  &  64  &  61  &  64  &  63  &  65  &  65  &  65  &  65  &  66  &  67  \\
	\hline
	\(max~m_5\)           &        &       &        &        &       &        &       &        &        &       &        &       &        &       &        &        &       &        &       &        &  53  \\
	\hline
\end{tabular}
